SAT Competition 2020\tnoteref{title}

### 2021-01-15 paper/main.tex
results update

Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
Despite its complexity, there is an ongoing progress in solving methods and their implementations in SAT solvers. 
The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.

SAT Competitions are organized regularly since 1992 in order to drive progress and to serve as a public assessment of the state-of-the-art in SAT solving. 
For each SAT Competition, a set of new benchmark instances is compiled which reflects the various applications of interest to the community.

In this competition, we initiated a new application-specific track. 
The idea is to provide a large amount of benchmark instances of a specific application and to evaluate all solvers with respect to these instance in a special track. 
In this competition, we used 200 instances of the planning domain to run a planning track.

Faster networks, distributed systems, and the increasing number of processors in modern computers show that the trend of increasing parallelism is about to continue.  
In the new cloud track, for the first time, solver authors could compete in SAT technologies that allow hundreds of SAT solvers to cooperate in solving a SAT instance.

\todo{Present some important pointers for SAT and CDCL}

@@

\todo{maybe mention \url{https://satcompetition.github.io/2020/}}

\todo{Maybe mention proceedings \cite{SC2020}}

@@

Instead of using or extending the DIMACS input format, we realize the Incremental track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may in general influence which questions will follow next.
% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!

@@

@@

For selection of benchmark instances in this competition, we used GBD Tools.%
\footnote{\url{https://pypi.org/project/gbd-tools/}} 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
The association of instance-id and instance attributes is maintained in publicly available databases.%
\footnote{\url{https://gbd.iti.kit.edu}}

GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Its databases provide information about all instances used in SAT competitive events dating back to 2006. 
In GBD Server, each instance also has an URL, such that instances can be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

@@

\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
\KwResult{$S$ : Set of Selected Instances}
\SetKwFunction{rand}{$\mathsf{random.choice}$}
\BlankLine
$S \leftarrow \emptyset$\;

\For {$a \in A$} {
	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
	\If {$|I_a^+|+|I_a^-| < 14$}{
		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
	}
	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
}
\Return $S$\;

@@

\begin{table}[t]
\small
\centering
\begin{tabular}{|l|l||rr|}
\hline
Family & Author & Submitted & Selected\\
\hline\hline
0-1 Integer Programming & Riveros & 6 & 2 \\
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
Cryptography & Paxian, Shaw, Soos & 106 & 34 \\
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Fermat & Riveros & 8 & 5 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Schur Coloring & Riveros & 4 & 2 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Sum Subset & Riveros & 5 & 2 \\
Tensors & Savicky & 20 & 14 \\
Termination & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\hline
\multicolumn{2}{|r||}{$\Sigma$} & 1260 & 300 \\
\hline
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

As can be seen in Table~\ref{tab:families}, a total of $28$ authors followed our calls for participation and benchmark instances, thus contributing a set of $1260$ previously unseen benchmark instances in a large variety of different instance families.

By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
In order to compile a balanced set of $300$ benchmark instances, we considered a maximum of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5--7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

@@

Table~\ref{tab:families} displays the numbers of submitted and selected instances grouped by problem family and author.

\begin{table}[t]
\centering
\begin{tabular}{|r|ccc|c|}
\hline
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\hline
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400\\
\hline
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

\begin{table}
\caption{Main SAT}
\label{tab:mainSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & CMS-ccnr \\
      & 3355.5 & 143 & Relaxed \\
      & 3721.2 & 139 & CMS-walksat \\
      & 3830.5 & 134 & Kissat \\
      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
      & 3909.6 & 135 & CaDiCaL-alluip \\
      & 4265.6 & 126 & CaDiCaL-trail \\
      & 4368.6 & 130 & CaDiCaL-sc2020 \\
      & 4804.9 & 114 & Kissat-unsat \\
      & 5173.2 & 110 & Undominated \\
      & 5206.0 & 110 & abcdsat\_n20 \\
      & 5244.1 & 107 & PADC\_DL \\   
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Planning (ALL)}
\label{tab:planning}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & CMS-ccnr \\
(2)   & 6472.9 & 79 & CMS-walksat \\
 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
      & 6650.1 & 79 & CaDiCaL-trail \\
      & 6713.0 & 75 & Maple\_Mix \\
      & 6746.5 & 75 & MapleCOMSPS\_init \\
      & 6754.3 & 73 & Maple\_Simp \\
      & 6773.0 & 73 & MapleCOMSPS\_drup \\
      & 6773.9 & 73 & Kissat-sat \\
      & 6774.2 & 73 & Kissat \\
      & 7003.0 & 69 & optsat\_m20 \\
      & 7025.5 & 68 & upGlucose3.0\_PADC \\
\end{tabular}
\end{table}

@@

\subsection{Best Tuples and Triples}

When selecting solvers for instance-specific algorithm selection, it is interesting to know about the complementarity of the performance of solvers. 
We created analyzed all pairs and triples of submitted solvers and calculated the PAR-2 score of the VBS of the resulting set of solvers.

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline
Solver 1 & Solver 2 & VBS score \\
\hline
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \\
\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat unsat} & \solver{CryptoMiniSat-CCAnr LSIDS} & \\
\solver{Kissat} & \solver{Relaxed Maple newTech} & \\
\hline
\end{tabular}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|}
\hline
Solver 1 & Solver 2 & Solver 3 & VBS score \\
\hline
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-Walksat} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{MapleCOMSPS\_LRB\_VSIDS\_2 init} &  \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-CCAnr} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip\_trail} & \\
\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip} & \\
\hline
\end{tabular}
\end{table}

>>>>

@@

@@

Instead of using or extending the DIMACS input format, we realize the Incremental Library track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may in general influence which questions will follow next.
% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!

@@

\todo{on wrong certificate (but still correct result) followed the demotion of the solver to the no-limits track}

@@

Benchmark instances selection in this competition was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
Instance attributes are maintained in publicly available databases, which provide information about all instances used in SAT Competitions since 2006.\footnote{\url{https://gbd.iti.kit.edu}} 
Benchmark instance identification also simplifies the distribution of instances via the GBD Server.\footnote{\url{https://gbd.iti.kit.edu/file/<gbd-hash>}}

@@

\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
\KwResult{$S$ : Set of Selected Instances}
\SetKwFunction{rand}{$\mathsf{random}$}
\BlankLine
$S \leftarrow \emptyset$\;

\For {$a \in A$} {
	$I_a^+ \leftarrow$ \rand{$7$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$}\;	
	$I_a^- \leftarrow$ \rand{$7$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$}\;	
	\If {$|I_a^+|+|I_a^-| < 14$}{
		$l \leftarrow 14 - |I_a^+| - |I_a^-|$\;
		$I_a^? \leftarrow$ \rand{$l$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$}\;
	}
	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
}
\Return $S$\;

@@

\begin{table}[t]
\small
\centering
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline
\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances of a large variety of different instance families. 
In order to compile a balanced set of $300$ benchmark instances, we first removed those instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances. 
We considered a maximum of $14$ submissions per author using the procedure which is depicted in Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (Lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown result (Lines~5--7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

@@

\begin{table}[t]
\centering
\begin{tabular}{rcccc}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

\begin{table}
\caption{Main SAT}
\label{tab:mainSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
(3)   & 3317.4 & 145 & CMS-ccnr \\
      & 3355.5 & 143 & Relaxed \\
      & 3721.2 & 139 & CMS-walksat \\
      & 3830.5 & 134 & Kissat \\
      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
      & 3909.6 & 135 & CaDiCaL-alluip \\
      & 4265.6 & 126 & CaDiCaL-trail \\
      & 4368.6 & 130 & CaDiCaL-sc2020 \\
   & 4804.9 & 114 & Kissat-unsat \\
   & 5173.2 & 110 & Undominated \\
   & 5244.1 & 107 & PADC\_DL \\
   & 5264.9 & 110 & f2trc-DL \\           
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Planning (ALL)}
\label{tab:planning}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline   
 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
(2)   & 6471.9 & 79 & CMS-ccnr \\
(2)   & 6472.9 & 79 & CMS-walksat \\
 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
      & 6650.1 & 79 & CaDiCaL-trail \\
      & 6713.0 & 75 & Maple\_Mix \\
      & 6746.5 & 75 & MapleCOMSPS\_init \\
      & 6754.3 & 73 & Maple\_Simp \\
      & 6773.0 & 73 & MapleCOMSPS\_drup \\
      & 6773.9 & 73 & Kissat-sat \\
      & 6774.2 & 73 & Kissat \\
      & 7025.5 & 68 & upGlucose3.0\_PADC \\
      & 7044.7 & 66 & Glucose3.0\_proofs \\
\end{tabular}
\end{table}

@@

\subsection{Small Portfolios}

\begin{table}[tb]
\centering
\begin{tabular}{lll}
\bf Solver 1 & \bf Solver 2 & \bf VBS\\
\hline\arrayrulecolor{lightgray}
\multirow{3}{*}{\solver{Kissat}} & \solver{CMS-CCAnr} & $3028.0$\\
 & \solver{CMS-CCAnr lsids} & $3052.8$\\
 & \solver{CMS-Walksat} & $3127.7$\\
\hline
\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-CCAnr}} & $3128.0$\\
\solver{CaDiCaL-alluip-trail} &  & $3128.0$\\
\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-Walksat}} & $3152.8$\\
\solver{CaDiCaL-alluip-trail} &  & $3152.9$\\
\hline
\solver{Kissat} & \multirow{2}{*}{\solver{Relaxed-newTech}} & $3177.7$\\
\solver{Kissat-unsat} &  & $3177.8$
\end{tabular}
\caption{The $9$ best performing tuples of solvers in terms of their VBS' PAR-2 score.}
\label{tab:best-tuples}
\end{table}

\begin{table}[tb]
\centering
\begin{tabular}{llll}
\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf VBS\\
\hline\arrayrulecolor{lightgray}
\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & $2827.7$\\
\hline
\multirow{3}{*}{\solver{Kissat}} & \multirow{3}{*}{\solver{CMS-CCAnr}} & \solver{Scavel01} & $2852.7$\\
 &  & \solver{f2trc-DL} & $2852.8$\\
 &  & \solver{DurianSat} & $2852.8$\\
\hline
\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{Scavel01}& $2877.6$\\
%\solver{Kissat-unsat} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{DurianSat} & $2877.8$\\
%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-CCAnr} & \solver{Kissat} & $2877.8$\\
\end{tabular}
\caption{The $5$ best performing triples of solvers in terms of their VBS' PAR-2 score.}
\label{tab:best-triples}
\end{table}

\begin{table}[tb]
\centering
\setlength\tabcolsep{4.5pt}
\begin{tabular}{lllll}
\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf Solver 4 & \bf VBS\\
\hline\arrayrulecolor{lightgray}
\multirow{2}{*}{\solver{Kissat}} & \multirow{2}{*}{\solver{CMS-CCAnr}} & \multirow{2}{*}{\solver{Scavel01}} & \solver{CaDiCaL-alluip} & 2727.7\\
 &  &  & \solver{CaDiCaL-alluip-trail} & 2727.7\\
\hline
\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & \solver{exp-V-LGB} & 2752.5\\
\hline
\solver{Kissat} & \solver{CaDiCaL-2020} & \solver{Scavel01} & \solver{Relaxed-newTech} & 2752.6\\
% & \solver{CMS-CCAnr lsids} & \solver{Scavel01} & \solver{f2trc-DL} & 2752.6
\end{tabular}
\caption{The $4$ best performing quatruples of solvers in terms of their VBS' PAR-2 score.}
\label{tab:best-quatruples}
\end{table}

The PAR-2 score of the VBS of all $48$ submitted solvers is $2701$. 
This is much better than the PAR-2 score of the single best solver (SBS) $3926$. 
In order to further analyze the contribution of solvers to the VBS, we calculated the PAR-2 score of the VBS of fixed-size subsets of the submitted solvers. 
In the following, we report on the best scores achieved by tuples, triples and quatruples of solvers in terms of their VBS's PAR-2 score.

The best scoring solver tuple is \solver{Kissat} and \solver{CryptoMiniSat-CCAnr}. 
The VBS of those two solvers achieved a PAR-2 score of $3028$. 
Further well performing solver tuples can be created from combinations of \solver{CaDiCaL-alluip} and \solver{CryptoMiniSat-CCAnr} or \solver{Kissat} and \solver{Relaxed-newTech}. 
A detailed report on the exact variants and scores of those solver tuples can be seen in Table~\ref{tab:best-tuples}.

The best triple of solvers is \solver{Kissat}, \solver{CryptoMiniSat-CCAnr lsids} and \solver{f2trc-DL}. 
In combination their VBS achieves a PAR-2 score of $2827.7$. 
Other combinations of \solver{Kissat} and \solver{CryptoMiniSat-CCAnr} with \solver{Scavel01} or \solver{DurianSat} achieved runner-up scores as can be seen in Table~\ref{tab:best-triples}.

With a PAR-2 score of $2727.7$ the solver quatruple \solver{Kissat}, \solver{CryptoMiniSat-CCAnr}, \solver{Scavel01} and \solver{CaDiCaL-alluip} is very close to the overall VBS. 
Runner-up and further best performing quatruples can be seen in Table~\ref{tab:best-quatruples}.
